Modelling the gas kinematics of an atypical Lyman-alpha emitting compact dwarf galaxy

### 2017-09-13 paper/paper.tex
add SLAE

\tol\ is a compact dwarf galaxy (CDG) that presents a
strong \lya emission with puzzling 
features: the line is highly symmetric, single peaked and broad 
\citep{Thuan97}.
This kind of profile also raises the question whether some high
redshift LAEs have asymmetric lines because the blue half was
truncated by the intergalactic medium \citep{2007MNRAS.377.1175D}. 
In this case the \lya radiation could emerge as a low surface
brightness glow, which may be connected to \lya halos, while also
influencing the way LAEs can be used as a probe of reionization
\citep[see the review by][and references therein]{2014PASA...31...40D}.

@@

Figure 1. Summarizes our main finding.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for the
multiphase model (thick line)  and the rotating homogeneous gas sphere
(thin line). 
The fit to the observations is not perfect. 
However, in spite of the
simplicity of our models, this is the first time that the main
\tol\ features can be reproduced: a broad, highly symmetric,
single-peaked \lya line.

@@

{\bf \tol\ presents a \lya emission line with puzzling features.}
Its flux at the line's center is high compared to other LAEs at low
redshift and the broad, highly symmetrical peak is virtually absent from other
LAEs at low and high redshift
\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
Simple shell models
fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by two different kinematic models: multiphase ISM and solid
body rotation.

@@

All in all, the mere existence of a strong LAE galaxy with a broad,
highly symmetric line is interesting. 
\tol's line shape is different to others and seems to reveal an
unexpected kinematic structure.
A confirmation of our results by new observations would support the multiphase model
as an element to be included in the study of \lya emitting
galaxies, {\bf consolidating the possibility to use the \lya line to
  constrain different models of star formation and feedback in the
  first generation of galaxies. }

>>>>

\tol\ is a compact dwarf galaxy (CDG) that presents a
strong \lya emission with puzzling 
features: the line is highly symmetric, single peaked and broad 
\citep{Thuan97}.
{\bf The existence of this Symmetric Lyman Alpha Emitter (SLAE)} raises the question whether some high
redshift LAEs have asymmetric lines because the blue half was
truncated by the intergalactic medium \citep{2007MNRAS.377.1175D}. 
In this case the \lya radiation could emerge as a low surface
brightness glow, which may be connected to \lya halos, while also
influencing the way LAEs can be used as a probe of reionization
\citep[see the review by][and references therein]{2014PASA...31...40D}.

@@

Figure 1. Summarizes our main finding.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for the
multiphase model (thick line)  and the rotating homogeneous gas sphere
(thin line). 
The fit to the observations is not perfect. 
However, in spite of the
simplicity of our models, this is the first time that the main
\tol\ features of {\bf this SLAE} can be reproduced: a broad, highly symmetric,
single-peaked \lya line.

@@

{\bf \tol\ presents a \lya emission line with puzzling features.}
Its flux at the line's center is high compared to other LAEs at low
redshift and the broad, highly symmetrical peak.
{\bf SLAEs are} virtually absent from other LAE surveys at low and high redshift
\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
Simple shell models
fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by two different kinematic models: multiphase ISM and solid
body rotation.

@@

All in all, the mere existence of {\bf a broad SLAE} is interesting.  
\tol's line shape is different to others and seems to reveal an
unexpected kinematic structure.
A confirmation of our results by new observations would support the multiphase model
as an element to be included in the study of \lya emitting
galaxies, {\bf consolidating the possibility to use the \lya line to
  constrain different models of star formation and feedback in the
  first generation of galaxies. }
